(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2014-11-22 ms/ms.tex
Made figure for germination day and updated ms.tex

\usepackage{geometry}
\geometry{letterpaper}
\usepackage[parfill]{parskip}    			% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{topcapt}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}

@@

\begin{document}
\maketitle

@@

% ANOVA table for LLL growth rate (need to label tables)
\begin{table*}[htbp]
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{ANOVA table, Longest leaf length growth} \\ \\
\begin{center}
\begin{tabular}{lcccccc}
\toprule

@@

\bottomrule
\end{tabular}
\end{center}
\end{table*}

% ANOVA table for height growth rate (need to label tables)
\begin{table*}[htbp]
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{ANOVA table, height growth} \\ \\
\begin{center}
\begin{tabular}{lcccccc}
\toprule

@@

\bottomrule
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}
\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_LLL_Lat.pdf}}
\label{fig:Fig1}
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{Figure \#} 
\end{figure*}

\begin{figure*}
\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_Height_Lat.pdf}}
\label{fig:Fig1}
\usefont{T1}{phv}{m}{n}
\fontsize{10}{12}
\selectfont
\textbf{Figure \#} 
\end{figure*}

>>>>

\usepackage{geometry}
\geometry{letterpaper}
\usepackage[parfill]{parskip}    			% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{topcapt}
\usepackage[labelfont =  {sf, bf}, textfont = sf, format = plain]{caption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}

% Make helvetica the default sans-serif font
\renewcommand\sfdefault{phv}

@@

\begin{document}
\maketitle
\listoffigures
\listoftables

@@

% ANOVA table for LLL growth rate (need to label tables)
\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, leaf expansion rate]{CAPTION}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

@@

	\bottomrule
	\end{tabular}
	\end{center}
\end{table}

% ANOVA table for height growth rate (need to label tables)
\begin{table}[htbp]
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[ANOVA table, stem expansion rate]{CAPTION}
	\begin{center}
	\begin{tabular}{lcccccc}
	\toprule

@@

	\bottomrule
	\end{tabular}
	\end{center}
\end{table}

@@

\begin{figure}[h!]
	\centerline{\includegraphics[width=0.5\textwidth]{Figures/Figure_DoG_Lat.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Southern populations germinate sooner.]{CAPTION}
	\label{fig:Fig_DoG}
\end{figure}

\begin{figure}[h!]
	\centerline{\includegraphics[width=0.5\textwidth]{Figures/Figure_LLL_Lat.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Southern populations grow faster (leaf expansion rate).]{CAPTION}
	\label{fig:Fig_LLL}
\end{figure}

\begin{figure}
	\centerline{\includegraphics[width=0.5\textwidth]{Figures/Figure_Height_Lat.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Southern populations grow faster (stem elongation rate).]{CAPTION}
	\label{fig:Fig_height}
\end{figure}
